Development of Performance Regression Analysis Tool using Distributed Tracing on Microservice-based Application\\

### 2022-06-23 paper.tex
txs auto checkin

There are two approaches that can be taken to solve the problem
performance regression \cite{regression-detection}, namely:
\begin{enumerate}
	\item Deteksi regresi dilakukan setelah aplikasi selesai dikembangkan dan di-\textit{deploy} pada lingkungan terdedikasi
	\item Deteksi regresi dilakukan sebelum aplikasi selesai dikembangkan dan di-\textit{deploy} dan melakukan studi terhadap perubahan yang dihasilkan pada \textit{source code}
\end{enumerate}

>>>>

There are two approaches that can be taken to solve the problem of performance regression \cite{regression-detection}, namely:
\begin{enumerate}
	\item Regression detection is carried out after the application has been developed and deployed in a dedicated environment:
	\item Regression detection is carried out before the application is developed and deployed, and then conducting a study of the resulting changes to the source code
\end{enumerate}
